---
title: "MJOLNIR_04_CovidMisconception"
author: "Léo HENRY"
date: "4/29/2022"
output: html_document
---


```{r}
library(questionr)
library(FactoMineR)
library(tidyverse)
library(psych)
library(GPArotation)
library(FactoMineR)
library(factoextra)
library(explor)
options(max.print=5001)
```


# data

```{r}
df <- read.csv("./data/mjolnir_clean_v5_AMBI_BIG5.csv")
```


# COV variables

```{r}
df %>% dplyr::select(matches("^COV((ATT)|(CONSP)|(ORIGIN)|(POLITICS)|(COVERAGE)|(ANTIVACC)|(MEDSKEP))"))
```


```{r}
df_covmis <- df %>%
  mutate(covmis_att_flu=COVATT_1,
         covmis_att_afrDie=7-COVATT_2,
         covmis_att_eldrNoBgDl=COVATT_3,
         covmis_att_rareNoWorr=COVATT_4,
         covmis_att_bgThrt=7-COVATT_5,
         covmis_cnsp_ctiusAsian=COVCONSP_1,
         covmis_cnsp_stpCovStpImmi=COVCONSP_2,
         covmis_cnsp_redIntWthChina=COVCONSP_3,
         covmis_cnsp_chnsCovRcst=7-COVCONSP_4,
         covmis_orgn_covPlnnd=COVORIGIN_1,
         covmis_orgn_covNat=7-COVORIGIN_2,
         covmis_orgn_covNgeenLab=COVORIGIN_3,
         covmis_orgn_scntFkNwsCov=COVORIGIN_4,
         covmis_pltc_polBgDlIntrst=COVPOLITICS_1,
         covmis_pltc_covNtSerPolSay=COVPOLITICS_2,
         covmis_pltc_polDwnplCovPlpLDngr=7-COVPOLITICS_3,
         covmis_cvrg_mdiaCovBgrDl=COVCOVERAGE_1,
         covmis_cvrg_nwsGdJbComCov=7-COVCOVERAGE_2,
         covmis_cvrg_mdiaUseCovMkTrmpRepLkBd=COVCOVERAGE_3,
         covmis_anti_frGovUseCovMndtVacc=COVANTIVACC_1,
         covmis_anti_thnksNoCovVacc=COVANTIVACC_2,
         covmis_anti_covVacEffRedVirus=7-COVANTIVACC_3,
         covmis_mdsk_medOrgUntrust=COVMEDSKEP_1,
         covmis_mdsk_skeptInfoDocSci=COVMEDSKEP_2,
         covmis_mdsk_medOrgRecBstInt=7-COVMEDSKEP_3,
         covmis_mdsk_fllwRecMedOrgImp=7-COVMEDSKEP_4)
```

### PCA analysis
```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_att")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```

```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_cnsp")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```



```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_orgn")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_pltc")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_cvrg")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```




```{r}
res.pca <- PCA(df_covmis %>% dplyr::select(matches("^covmis_anti")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```



### HCPM ET CLASSIF 

```{r}
res.mfa <- MFA(df_covmis %>% dplyr::select(matches("^covmis")) %>% rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}),
               group = c(5,4,4,3,3,3,4),
               type=c("c","c","c","c","c","c","c"),
               name.group = c("att","conspiracy","origin","politics","coverage","antivaccin", "Mdsk"))
```


```{r}
get_eigenvalue(res.mfa) %>% head
```

```{r}
fviz_screeplot(res.mfa)
```


```{r}
group <- get_mfa_var(res.mfa, "group")

group$coord
group$contrib
# Contribution to the first dimension
fviz_contrib(res.mfa, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa, "group", axes = 2)
```



```{r}
quanti.var <- get_mfa_var(res.mfa, "quanti.var")
quanti.var$contrib
quanti.var$coord
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")
# Contributions to dimension 1
fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
# Contributions to dimension 2
fviz_contrib(res.mfa, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")
```



#### Classification

```{r}
res.hcpc <- HCPC(res.mfa, nb.clust=4, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$quanti
```

```{r}
save(res.mfa, res.hcpc, file='./data/mfa_and_classification.rdata')
```


#### Analysis

```{r}
df_covmis$cov_class <- res.hcpc$data.clust$clust
freq(df_covmis$cov_class)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  ggplot(., aes(y=Covmis_res, x= cov_class, fill=cov_class)) +
  geom_boxplot() +
  facet_wrap(~ Covmis_var, ncol = 5)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_")) %>%
  ggplot(., aes(y=Covmis_res, x= Covmis_var, fill=Covmis_var)) +
  geom_boxplot() +
  facet_wrap(~ cov_class, ncol = 1)
```


```{r}
table(df_covmis$EXPGRP_TEXT, df_covmis$cov_class) %>% cprop
table(df_covmis$EXPGRP_TEXT, df_covmis$cov_class) %>% chisq.test()
```

```{r}
table(df_covmis$CONTINENT_BORN_TEXT_3, df_covmis$cov_class) %>% lprop
```

```{r}
table(df_covmis$HAS_LIVED_USA, df_covmis$cov_class) %>% lprop
```

By considering the data has quatitative and not qualitative we tend to put closer the outsider that might have answered with extreme response in misconsception data and those who answered in the middle. Let's try to see if we get different result when analysing qualitative data.

### MFA and HCPC with qualitative data



```{r}
res_mfa_quali <- df_covmis %>%
  dplyr::select(matches("^covmis_")) %>%
  transmute_all(~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>% 
  rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}) %>%
  MFA(.,
      group = c(5,4,4,3,3,3,4),
      type=c("n","n","n","n","n","n","n"),
      name.group = c("att","conspiracy","origin","politics","coverage","antivaccin","Mdsk"))
```



```{r}
fviz_screeplot(res_mfa_quali)
```



```{r}
fviz_mfa_var(res_mfa_quali, "quali.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
```


```{r}
quali.var <- get_mfa_var(res_mfa_quali, "quali.var")
quali.var$coord
quali.var$contrib
```


#### Cassification

```{r}
res.hcpc <- HCPC(res_mfa_quali, nb.clust=3, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$category
```

```{r}
save(res_mfa_quali, res.hcpc, file='./data/mfa_and_classification_onqualidata.rdata')
```


#### Analysis

##### Boxplot of choice covmis per group

```{r}
df_covmis$covqual_class <- res.hcpc$data.clust$clust
freq(df_covmis$covqual_class)

df_covmis %>%
  transmute_at(.vars = vars(starts_with("covmis")),
               ~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>%
  cbind(df,.) %>%
  mutate(covqual_class=res.hcpc$data.clust$clust) %>%
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_"),
         Covmis_res=factor(Covmis_res,
                           levels = c("+","=","-"))) %>%
  ggplot(., aes(x = covqual_class, fill=Covmis_res)) +
  scale_fill_manual(values=c("green", "blue", "red")) +
  geom_bar(position='fill') +
  facet_wrap(~ Covmis_var, ncol = 5)
```

##### mean of choice covmis per group

```{r}
df_mean_per_cat <- df_covmis %>%
  dplyr::select(matches("^covmis_")) %>%
  mutate(covmis_cat=df_covmis$covqual_class) %>%
  group_by(covmis_cat) %>%
  summarise_all(mean)
df_mean_per_cat
```


####

```{r}
questionr::freq(df_covmis$covmis_cat)
```



```{r}
df_covmis$HH_INCOME_TEXT <- fct_recode(df$HH_INCOME %>% as.character,
"Less than $10,000"="1",
"$10,000 to $30,000"="2",
"$30,000 to $50,000"="3",
"$50,000 to $70,000"="4",
"$70,000 to $100,000"="5",
"$100,000 to $200,000"="6",
"$200,000 to $500,000"="7",
"$500,000 or more"="8")
table(df_covmis$HH_INCOME_TEXT, df_covmis$covqual_class) %>% cprop %>% xtable::xtable()
```


### Demo cluster

```{r}
table(df_covmis$demo_class, df_covmis$covqual_class) %>% cprop
table(df_covmis$demo_class, df_covmis$covqual_class) %>% t.test()

```


## Logistiaue regression

```{r}
library(ordinal)
library(nnet)
library(GGally)
library(gtsummary)
library(ggeffects)
library(rstatix)
```


We'll do it on the demo classification and then on the other demographic data


```{r}
df_covmis$covqual_class <- factor(df_covmis$covqual_class, c("1","2","3"))
freq(df_covmis$covqual_class)
```


```{r}
df_covmis$demo_class <- df_covmis$demo_class %>% as.factor()
regm <- clm(covqual_class ~ demo_class, data = df_covmis)
summary(regm)
```


```{r}
tbl_regression(regm, exponentiate = TRUE)
```



```{r}
ggcoef_model(
  regm,
  exponentiate = TRUE
)
```


```{r}
plot(ggeffect(regm, "demo_class"))
```



```{r}
df_covmis$covqual_class <-  df_covmis$covqual_class %>%
  as.character() %>%
  as.numeric()
ggpubr::ggboxplot(df_covmis, x="demo_class", y="covqual_class")
res.aov <- anova_test(covqual_class ~ demo_class, data = df_covmis)
res.aov
pwc <- df_covmis %>% tukey_hsd(covqual_class ~ demo_class)
pwc
pwc <- pwc %>% add_xy_position(x = "demo_class")
ggpubr::ggboxplot(df_covmis, x = "demo_class", y = "covqual_class") +
  ggpubr::stat_pvalue_manual(pwc, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )
```

```{r}
df_covmis$covqual_class <- factor(df_covmis$covqual_class, c("1","2","3"))
freq(df_covmis$covqual_class)
```


```{r}
df_covmis$CONTINENT_BORN_TEXT_1 <- relevel(df_covmis$CONTINENT_BORN_TEXT_1 %>% as.factor(), "USA")
df_covmis$DOB_YEAR_PERIODE <- relevel(df_covmis$DOB_YEAR_PERIODE %>% as.factor(), "(1995,2005]")
df_covmis$EDUCATION_2_TEXT <- fct_recode(df$EDUCATION_1 %>% as.character,
          "No college degree"="1",
          "No college degree"="2",
          "No college degree"="3",
          "College degree"="4",
          "College degree"="5",
          "Graduate degree"="6",
          "Graduate degree"="7",
          "Graduate degree"="8")
df_covmis$EDUCATION_2_TEXT %>% freq()

regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + DOB_YEAR_PERIODE + SEX_TEXT + EDUCATION_2_TEXT, data = df_covmis)
summary(regm)
```


```{r}
tbl_regression(regm, exponentiate = TRUE)
```



```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

```{r}
f_normfactor <- function(v){
  res <- AMBI::f_normalisation(v)
  res <- res*3
  res <- cut(res, c(0,1,2,3), labels=c('weak','middle','high'))
  return(res)
}
```



```{r}
df_covmis$neuroticism_qual <- f_normfactor(df_covmis$AMBI_BIG5_Neuroticism)
df_covmis$extraversion_qual <- f_normfactor(df_covmis$AMBI_BIG5_Extraversion)
df_covmis$openness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Openness)
df_covmis$conscientiousness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Conscientiousness)
df_covmis$agreeableness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Agreeableness)
df_covmis$covqual_class <- relevel(df_covmis$covqual_class %>% as.factor(), "2")


regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + DOB_YEAR_PERIODE + SEX_TEXT + EDUCATION_2_TEXT + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)
summary(regm)
```

```{r}
table(df_covmis$EDUCATION_2_TEXT, df_covmis$EXPGRP_TEXT) %>% lprop() %>% xtable::xtable()
```


```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

the variable on the age is long, we shall try to shorten it and cross it with education variable (young people without a college degree are socially different than older on without a college degree)

```{r}
df_covmis$DOB_YEAR_PERIODE <- df_covmis$DOB_YEAR %>% cut(breaks = c(1944,1955,1965,1975,1985,1995,2005))
df_covmis$DOB_AGE_BRACKET <- fct_recode(df_covmis$DOB_YEAR_PERIODE %>% as.character,
          "-25y"="(1995,2005]",
          "25 - 45y"="(1985,1995]",
          "25 - 45y"="(1975,1985]",
          "+45y"="(1944,1955]", 
          "+45y"="(1955,1965]",
          "+45y"="(1965,1975]")
df_covmis <-  df_covmis %>% unite("age_education", c("DOB_AGE_BRACKET","EDUCATION_2_TEXT"))
df_covmis$age_education <- factor(df_covmis$age_education, levels=c('-25y_No college degree',
                                                    "25 - 45y_No college degree",
                                                    '+45y_No college degree', 
                                                    "-25y_College degree", 
                                                    "25 - 45y_College degree",
                                                    "+45y_College degree",
                                                    "-25y_Graduate degree",
                                                    "25 - 45y_Graduate degree",
                                                    "+45y_Graduate degree"))
regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT + age_education + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)
summary(regm)
```

```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

Now we shall consider only two groups, those in the first and second group, and those in the third group.

```{r}
df_covmis$covqual_class_2 <- fct_recode(df_covmis$covqual_class %>% as.character,
          "Believers"="1",
          "Believers"="2",
          "Skeptics"="3")
freq(df_covmis$covqual_class_2)

reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             age_education + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, data = df_covmis, family = binomial(logit))
reg
```


```{r}
ggcoef_model(reg, exponentiate = TRUE)
```

```{r}
which(is.na(df_covmis$extraversion_qual))
```

```{r}
df_covmis[585,]
```

```{r}
df_covmis2 <-  df_covmis %>% filter((!is.na(CONTINENT_BORN_TEXT_1))) %>%
  filter((!is.na(neuroticism_qual))) %>%
  filter((!is.na(extraversion_qual))) %>%
  filter((!is.na(openness_qual))) %>%
  filter((!is.na(conscientiousness_qual))) %>%
  filter((!is.na(agreeableness_qual)))
which(is.na(df_covmis2 %>% dplyr::select(EXPGRP_TEXT, CONTINENT_BORN_TEXT_1, HAS_LIVED_USA, SEX_TEXT,
             age_education, neuroticism_qual, extraversion_qual, openness_qual, 
             conscientiousness_qual, agreeableness_qual)), arr.ind=TRUE)
```

```{r}
df_covmis$CONTINENT_BORN_TEXT_1 %>% levels()
df_covmis$CONTINENT_BORN_TEXT_1 %>% levels()

```


```{r}
reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             age_education + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, 
           data = df_covmis2, 
           family = binomial(logit))
step(reg)
```

```{r}
reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + HAS_LIVED_USA + openness_qual, 
           data = df_covmis2, 
           family = binomial(logit))
ggcoef_model(reg, exponentiate = TRUE)
```

```{r}
df_covmis2$EDUCATION_2_TEXT <- fct_recode(df_covmis2$EDUCATION_1 %>% as.character,
          "No college degree"="1",
          "No college degree"="2",
          "No college degree"="3",
          "College degree"="4",
          "College degree"="5",
          "Graduate degree"="6",
          "Graduate degree"="7",
          "Graduate degree"="8")
df_covmis2$DOB_AGE_BRACKET <- fct_recode(df_covmis2$DOB_YEAR_PERIODE %>% as.character,
          "-25y"="(1995,2005]",
          "25 - 45y"="(1985,1995]",
          "25 - 45y"="(1975,1985]",
          "+45y"="(1944,1955]", 
          "+45y"="(1955,1965]",
          "+45y"="(1965,1975]")
regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             EDUCATION_2_TEXT + DOB_AGE_BRACKET + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, 
           data = df_covmis2)
step(regm)
```



```{r}
regm <- multinom(covqual_class ~ EXPGRP_TEXT + HAS_LIVED_USA + 
    SEX_TEXT + openness_qual + agreeableness_qual, 
           data = df_covmis2)
stargazer::stargazer(regm)
ggcoef_multinom(regm, exponentiate = TRUE)
```


### Let's reduce the size of our data

```{r}
df_covmis$EDUCATION_2_TEXT <- fct_recode(df_covmis$EDUCATION_1 %>% as.character,
          "No college degree"="1",
          "No college degree"="2",
          "No college degree"="3",
          "College degree"="4",
          "College degree"="5",
          "Graduate degree"="6",
          "Graduate degree"="7",
          "Graduate degree"="8")

df_covmis$DOB_AGE_BRACKET <- fct_recode(df_covmis$DOB_YEAR_PERIODE %>% as.character,
          "-25y"="(1995,2005]",
          "25 - 45y"="(1985,1995]",
          "25 - 45y"="(1975,1985]",
          "+45y"="(1944,1955]", 
          "+45y"="(1955,1965]",
          "+45y"="(1965,1975]") %>%
  relevel("-25y")

df_covmis$HH_INCOME_TEXT2 <- fct_recode(df$HH_INCOME %>% as.character,
"Less than $30,000"="1",
"Less than $30,000"="2",
"$30,000 to $70,000"="3",
"$30,000 to $70,000"="4",
"$70,000 or more"="5",
"$70,000 or more"="6",
"$70,000 or more"="7",
"$70,000 or more"="8")

df_covmis$covqual_class <- relevel(df_covmis$covqual_class, "1")


df_covmis3 <- df_covmis %>%
                   filter(EXPGRP_TEXT != "Non-Chinese Asian" &
                            !(CONTINENT_BORN_TEXT_1 %in% c("4Tigers and Japan", "Africa", "Middle East",
                                                           "North America", "Oceania", "South America")) &
                            !(is.na(CONTINENT_BORN_TEXT_1)) &
                            !(SEX_TEXT %in% c("Other", "Transgender")) &
                            HH_INCOME_TEXT != "$500,000 or more")

df_covmis3$CONTINENT_BORN_TEXT_1 <- df_covmis3$CONTINENT_BORN_TEXT_1 %>% as.character %>% as.factor %>% relevel("USA")

regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + DOB_AGE_BRACKET + SEX_TEXT + EDUCATION_2_TEXT + HH_INCOME_TEXT2 + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, 
                 data = df_covmis3)
summary(regm)

table(df_covmis$EDUCATION_2_TEXT, df_covmis$EXPGRP_TEXT) %>% lprop() %>% xtable::xtable()

ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```




# Create a quantitative variable of covid skeptism

options:
  - Sem scoring on latent variable 
  - Coordinate on the first variable of MFA which resume almost 50% of the variance
  - Standardization of score

## SEM Scoring for covid skepticism

```{r}
library(questionr)
library(FactoMineR)
library(tidyverse)
library(lavaan)
library(semTools)
library(lavaanPlot)
library(MVN)
library(MIIVsem)
options(max.print=2000)
```
'
Attention =~ covmis_att_flu + covmis_att_afrDie + covmis_att_eldrNoBgDl + covmis_att_rareNoWorr + covmis_att_bgThrt
Conspiracy =~ covmis_cnsp_ctiusAsian + covmis_cnsp_stpCovStpImmi + covmis_cnsp_redIntWthChina + covmis_cnsp_chnsCovRcst
Origin =~ covmis_orgn_covPlnnd + covmis_orgn_covNat + covmis_orgn_covNgeenLab + covmis_orgn_scntFkNwsCov
Politics =~ covmis_pltc_polBgDlIntrst + covmis_pltc_covNtSerPolSay + covmis_pltc_polDwnplCovPlpLDngr
Coverage =~ covmis_cvrg_mdiaCovBgrDl + covmis_cvrg_nwsGdJbComCov + covmis_cvrg_mdiaUseCovMkTrmpRepLkBd
AntiVacc =~ covmis_anti_frGovUseCovMndtVacc + covmis_anti_thnksNoCovVacc + covmis_anti_covVacEffRedVirus
MedSkep =~ covmis_mdsk_medOrgUntrust + covmis_mdsk_skeptInfoDocSci + covmis_mdsk_medOrgRecBstInt + covmis_mdsk_fllwRecMedOrgImp
Attention ~~ Conspiracy
Attention ~~ Origin
Attention ~~ Politics
Attention ~~ Coverage
Attention ~~ AntiVacc
Attention ~~ MedSkep
Conspiracy ~~ Origin
Conspiracy ~~ Politics
Conspiracy ~~ Coverage
Conspiracy ~~ AntiVacc
Conspiracy ~~ MedSkep
Origin ~~ Politics
Origin ~~ Coverage
Origin ~~ AntiVacc
Origin ~~ MedSkep
Politics ~~ Coverage
Politics ~~ AntiVacc
Politics ~~ MedSkep
Coverage ~~ AntiVacc
Coverage ~~ MedSkep
AntiVacc ~~ MedSkep
CovidSkepticism =~ Attention + Conspiracy + Origin + Politics + Coverage + AntiVacc + MedSkep
'
```{r}
model <- '
CovidSkepticism =~ covmis_att_flu + covmis_att_afrDie + covmis_att_eldrNoBgDl + covmis_att_rareNoWorr + covmis_att_bgThrt + covmis_cnsp_ctiusAsian + covmis_cnsp_stpCovStpImmi + covmis_cnsp_redIntWthChina + covmis_cnsp_chnsCovRcst + covmis_orgn_covPlnnd + covmis_orgn_covNat + covmis_orgn_covNgeenLab + covmis_orgn_scntFkNwsCov + covmis_pltc_polBgDlIntrst + covmis_pltc_covNtSerPolSay + covmis_pltc_polDwnplCovPlpLDngr + covmis_cvrg_mdiaCovBgrDl + covmis_cvrg_nwsGdJbComCov + covmis_cvrg_mdiaUseCovMkTrmpRepLkBd + covmis_anti_frGovUseCovMndtVacc + covmis_anti_thnksNoCovVacc + covmis_anti_covVacEffRedVirus + covmis_mdsk_medOrgUntrust + covmis_mdsk_skeptInfoDocSci + covmis_mdsk_medOrgRecBstInt + covmis_mdsk_fllwRecMedOrgImp
'
```

```{r}
fit <- cfa(model, data = df_covmis, estimator = "ML")
semPlot::semPaths(fit)
```

```{r}
summary(fit, fit.measures=T, standardized=T, rsquare=T) 
```


```{r}
fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  filter(!(rhs%in%lhs)) %>% 
  group_by(lhs) %>%
  summarise(sest=sum(est)) %>%
  inner_join(fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
    filter((rhs%in%lhs)) %>% 
    dplyr::select(rhs,est),
  by = c("lhs" = "rhs")) %>%
  mutate(factor=sest*est) %>%
  dplyr::select(factor) %>%
  colSums()
```



```{r}
f_semscoring_latent <- function(fit, data, scaled = TRUE){
  
  df_sem_estimate <- fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1)
  v_latent_var <- df_sem_estimate$lhs %>% as_factor %>% levels
  
  f_calculate_latent <- function(latent_var, data2){
    
    v_obs_var <- df_sem_estimate %>% filter(lhs==latent_var) %>% dplyr::select(rhs) %>% as_vector()
    
    d <- tibble(matrix(ncol = 0, nrow = nrow(data)))
    for (obs_var in v_obs_var) {
      res <- data2[,obs_var] * (df_sem_estimate %>% filter(lhs==latent_var, rhs==obs_var) %>% dplyr::select(est) %>% as.numeric())
      d[,obs_var] <- res
    }
    res <- rowSums(d)
    if(scaled) res <- res %>% scale
    return(res)
  }
  
  d <- tibble(matrix(ncol = 0, nrow = nrow(data)))
  for(j in v_latent_var){
    data[,j] <- f_calculate_latent(j, data)
  }
  data <- data %>% dplyr::select(v_latent_var)
  return(data)
}


df_scorecovmis <- f_semscoring_latent(fit, df_covmis, scaled = F)

(df_scorecovmis$CovidSkepticism == min(df_scorecovmis$CovidSkepticism)) %>% which()
df_covmis %>% dplyr::select(matches("^covmis")) %>% as_tibble %>% dplyr::slice(455L,589L)
```


```{r}
standardisation_hierar <- function(x){
  x <-  (x- (fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  filter(!(rhs%in%lhs)) %>% 
  group_by(lhs) %>%
  summarise(sest=sum(est)) %>%
  inner_join(fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
    filter((rhs%in%lhs)) %>% 
    dplyr::select(rhs,est),
  by = c("lhs" = "rhs")) %>%
  mutate(factor=sest*est) %>%
  dplyr::select(factor) %>%
  colSums()))  / (fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  filter(!(rhs%in%lhs)) %>% 
  group_by(lhs) %>%
  summarise(sest=sum(est)) %>%
  inner_join(fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
    filter((rhs%in%lhs)) %>% 
    dplyr::select(rhs,est),
  by = c("lhs" = "rhs")) %>%
  mutate(factor=sest*est) %>%
  dplyr::select(factor) %>%
  colSums() * 6) * 100
}

standardisation <- function(x){
  x <-  (x- (fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  dplyr::select(est) %>%
  colSums()))  / ((fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  dplyr::select(est) %>%
  colSums()) * 6) * 100
}

df_scorecovmis$CovidSkepticism <- df_scorecovmis$CovidSkepticism %>% standardisation()
df_covmis$CovidSkepticism <- df_scorecovmis$CovidSkepticism
df_covmis$CovidSkepticism %>% summary

```

```{r}
df_covmis$CovidSkepticism %>% hist()
```

```{r}
write.csv(df_covmis,"./data/mjolnir_clean_v6_Covmis.csv")
```

### cleaning data

Some group of participants are not big enough to be analyzed and produces noises we want to avoid.

```{r}
df_covmis$HH_INCOME_TEXT2 <- fct_recode(df$HH_INCOME %>% as.character,
"Less than $30,000"="1",
"Less than $30,000"="2",
"$30,000 to $70,000"="3",
"$30,000 to $70,000"="4",
"$70,000 or more"="5",
"$70,000 or more"="6",
"$70,000 or more"="7",
"$70,000 or more"="8")
df_covmis$EDUCATION_2_TEXT <- fct_recode(df$EDUCATION_1 %>% as.character,
          "No college degree"="1",
          "No college degree"="2",
          "No college degree"="3",
          "College degree"="4",
          "College degree"="5",
          "Graduate degree"="6",
          "Graduate degree"="7",
          "Graduate degree"="8")
df_covmis$DOB_YEAR_PERIODE <- df_covmis$DOB_YEAR %>% cut(breaks = c(1944,1955,1965,1975,1985,1995,2005))
df_covmis$DOB_AGE_BRACKET <- fct_recode(df_covmis$DOB_YEAR_PERIODE %>% as.character,
          "-25y"="(1995,2005]",
          "25 - 35y"="(1985,1995]",
          "35 - 45y"="(1975,1985]",
          "+45y"="(1944,1955]", 
          "+45y"="(1955,1965]",
          "+45y"="(1965,1975]")
f_normfactor <- function(v){
  res <- AMBI::f_normalisation(v)
  res <- res*3
  res <- cut(res, c(-0.1,1,2,3), labels=c('weak','middle','high'))
  return(res)
}
df_covmis$neuroticism_qual <- f_normfactor(df_covmis$AMBI_BIG5_Neuroticism)
df_covmis$extraversion_qual <- f_normfactor(df_covmis$AMBI_BIG5_Extraversion)
df_covmis$openness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Openness)
df_covmis$conscientiousness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Conscientiousness)
df_covmis$agreeableness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Agreeableness)



df_covmis2 <-  df_covmis %>%
  filter(EXPGRP_TEXT != "Non-Chinese Asian" &
           !(CONTINENT_BORN_TEXT_1 %in% c("4Tigers and Japan", "Africa", "Middle East",
                                        "North America", "Oceania", "South America")) &
           !(is.na(CONTINENT_BORN_TEXT_1)) &
           !(SEX_TEXT %in% c("Other", "Transgender")) &
           HH_INCOME_TEXT != "$500,000 or more") 

df_covmis2 %>%
  dplyr::select(EXPGRP_TEXT) %>%
  freq()
  
df_covmis2 %>%
  dplyr::select(CONTINENT_BORN_TEXT_1) %>%
  freq()

df_covmis2 %>%
  dplyr::select(SEX_TEXT) %>%
  freq()

df_covmis2 %>%
  dplyr::select(agreeableness_qual) %>%
  freq()

df_covmis2 %>%
  dplyr::select(conscientiousness_qual) %>%
  freq()
```


```{r}
ex <- car::powerTransform(df_covmis2$CovidSkepticism+0.0000001)
df_covmis2$CovidSkepticism^ex$lambda %>% hist()
df_covmis2$CovidSkepticismnorm <-  df_covmis2$CovidSkepticism^ex$lambda
```




```{r}
df_covmis2 %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  ggplot(aes(Covmis_res, CovidSkepticism)) +
  geom_point() +
  geom_smooth(method = "loess") + 
  facet_wrap(~ Covmis_var, ncol = 5)
```


```{r}
library(ggpubr)

res <-  list()

res[["aov"]] <- df_covmis2 %>% anova_test(CovidSkepticism ~ EXPGRP_TEXT)
pwc <- df_covmis2 %>% tukey_hsd(CovidSkepticism ~ EXPGRP_TEXT)
res[["pwc"]] <- pwc
pwc <- res[["pwc"]] %>% add_xy_position(x = "EXPGRP_TEXT")

ggboxplot(df_covmis2, x = "EXPGRP_TEXT", y = "CovidSkepticism") +
        stat_pvalue_manual(pwc, hide.ns = TRUE) +
        labs(subtitle = get_test_label(res[["aov"]], detailed = TRUE),
             caption = get_pwc_label(pwc))
```


```{r}

res <-  list()

res[["aov"]] <- df_covmis2 %>% anova_test(CovidSkepticism ~ EDUCATION_2_TEXT)
pwc <- df_covmis2 %>% tukey_hsd(CovidSkepticism ~ EDUCATION_2_TEXT)
res[["pwc"]] <- pwc
pwc <- res[["pwc"]] %>% add_xy_position(x = "EDUCATION_2_TEXT")

ggboxplot(df_covmis2, x = "EDUCATION_2_TEXT", y = "CovidSkepticism") +
        stat_pvalue_manual(pwc, hide.ns = TRUE) +
        labs(subtitle = get_test_label(res[["aov"]], detailed = TRUE),
             caption = get_pwc_label(pwc))
```


```{r}

res <-  list()

res[["aov"]] <- df_covmis2 %>% anova_test(CovidSkepticism ~ SEX_TEXT)
pwc <- df_covmis2 %>% tukey_hsd(CovidSkepticism ~ SEX_TEXT)
res[["pwc"]] <- pwc
pwc <- res[["pwc"]] %>% add_xy_position(x = "SEX_TEXT")

ggboxplot(df_covmis2, x = "SEX_TEXT", y = "CovidSkepticism") +
        stat_pvalue_manual(pwc, hide.ns = TRUE) +
        labs(subtitle = get_test_label(res[["aov"]], detailed = TRUE),
             caption = get_pwc_label(pwc))
```


```{r}
df_covmis2 %>%
  gather(key = "BIG5_var", value="BIG5_res", df_covmis %>% colnames %>% str_detect("BIG5") %>% which) %>%
  ggplot(aes(BIG5_res, CovidSkepticism)) +
    facet_wrap(~BIG5_var) +
    geom_point(color="grey") +
    geom_smooth(method='lm')+
    ggpubr::stat_regline_equation(label.y = 100, aes(label = ..eq.label..)) +
    ggpubr::stat_regline_equation(label.y = 90, aes(label = ..rr.label..)) +
    ggpmisc::stat_fit_glance(method = 'lm',
                       method.args = list(formula = formula),
                       geom = 'text',
                       aes(label = paste("p = ", signif(..p.value.., digits = 3), sep = "")),
                       label.x.npc = 'left', size = 3)
```



```{r}
res.aov <- rstatix::anova_test(CovidSkepticismnorm ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HH_INCOME_TEXT2 + SEX_TEXT + EDUCATION_2_TEXT + DOB_AGE_BRACKET + AMBI_BIG5_Neuroticism + AMBI_BIG5_Extraversion + AMBI_BIG5_Openness + AMBI_BIG5_Conscientiousness + AMBI_BIG5_Agreeableness, data = df_covmis2)
res.aov
res.aov <- rstatix::anova_test(CovidSkepticismnorm ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HH_INCOME_TEXT2 + SEX_TEXT + EDUCATION_2_TEXT:DOB_AGE_BRACKET, data = df_covmis2)
res.aov
res.aov <- rstatix::anova_test(CovidSkepticismnorm ~ AMBI_BIG5_Neuroticism + AMBI_BIG5_Extraversion + AMBI_BIG5_Openness + AMBI_BIG5_Conscientiousness + AMBI_BIG5_Agreeableness, data = df_covmis2)
res.aov
```

```{r}
pwc <- df_covmis2 %>% tukey_hsd(CovidSkepticismnorm ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HH_INCOME_TEXT2 + SEX_TEXT + EDUCATION_2_TEXT + DOB_AGE_BRACKET)
pwc[,-c(1)] %>% xtable::xtable()

res.aov <- anova_test(CovidSkepticismnorm ~ EXPGRP_TEXT , data = df_covmis2)
res.aov
pwc <- df_covmis2 %>% tukey_hsd(CovidSkepticismnorm ~ EXPGRP_TEXT)
pwc
```

```{r}
res.aov <- rstatix::anova_test(CovidSkepticismnorm ~ demo_class + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis2)

res.aov
```

```{r}
df_covmis2 <- fastDummies::dummy_cols(df_covmis2, select_columns = c("EXPGRP_TEXT","CONTINENT_BORN_TEXT_1", 'HH_INCOME_TEXT2', "SEX_TEXT", "EDUCATION_2_TEXT", "DOB_AGE_BRACKET"))

colnames(df_covmis2) <- str_replace_all(colnames(df_covmis2), "[ ,+$-]", "")

res.aov <- anova_test(CovidSkepticismnorm ~ EXPGRP_TEXT_Chinese + EXPGRP_TEXT_White + CONTINENT_BORN_TEXT_1_CentralEasternEurope + CONTINENT_BORN_TEXT_1_DeveloppingAsia + CONTINENT_BORN_TEXT_1_USA + CONTINENT_BORN_TEXT_1_WesternEurope + HH_INCOME_TEXT2_Lessthan30000 + HH_INCOME_TEXT2_30000to70000 + HH_INCOME_TEXT2_70000ormore + SEX_TEXT_Female + SEX_TEXT_Male + EDUCATION_2_TEXT_Nocollegedegree + EDUCATION_2_TEXT_Collegedegree + EDUCATION_2_TEXT_Graduatedegree + DOB_AGE_BRACKET_45y + DOB_AGE_BRACKET_3545y + DOB_AGE_BRACKET_2535y + DOB_AGE_BRACKET_25y + AMBI_BIG5_Neuroticism + AMBI_BIG5_Extraversion + AMBI_BIG5_Openness + AMBI_BIG5_Conscientiousness + AMBI_BIG5_Agreeableness, data = df_covmis2)
res.aov
```

```{r}
df_covmis2$demo_class %>% freq()
```


#### What if without conspiracy and xenophobia question

```{r}
model <- '
Attention =~ covmis_att_flu + covmis_att_afrDie + covmis_att_eldrNoBgDl + covmis_att_rareNoWorr + covmis_att_bgThrt
Origin =~ covmis_orgn_covPlnnd + covmis_orgn_covNat + covmis_orgn_covNgeenLab + covmis_orgn_scntFkNwsCov
Politics =~ covmis_pltc_polBgDlIntrst + covmis_pltc_covNtSerPolSay + covmis_pltc_polDwnplCovPlpLDngr
Coverage =~ covmis_cvrg_mdiaCovBgrDl + covmis_cvrg_nwsGdJbComCov + covmis_cvrg_mdiaUseCovMkTrmpRepLkBd
AntiVacc =~ covmis_anti_frGovUseCovMndtVacc + covmis_anti_thnksNoCovVacc + covmis_anti_covVacEffRedVirus
CovidSkepticism2 =~ Attention + Origin + Politics + Coverage + AntiVacc
'
fit <- cfa(model, data = df_covmis, estimator = "ML")
df_scorecovmis <- f_semscoring_latent(fit, df_covmis, scaled = F)
standardisation <- function(x){
  x <-  (x- (fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  filter(!(rhs%in%lhs)) %>% 
  group_by(lhs) %>%
  summarise(sest=sum(est)) %>%
  inner_join(fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
    filter((rhs%in%lhs)) %>% 
    dplyr::select(rhs,est),
  by = c("lhs" = "rhs")) %>%
  mutate(factor=sest*est) %>%
  dplyr::select(factor) %>%
  colSums()))  / (fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
  filter(!(rhs%in%lhs)) %>% 
  group_by(lhs) %>%
  summarise(sest=sum(est)) %>%
  inner_join(fit %>% lavaan::partable() %>% as_tibble %>% filter(user==1) %>%
    filter((rhs%in%lhs)) %>% 
    dplyr::select(rhs,est),
  by = c("lhs" = "rhs")) %>%
  mutate(factor=sest*est) %>%
  dplyr::select(factor) %>%
  colSums() * 6) * 100
}
df_scorecovmis$CovidSkepticism <- df_scorecovmis$CovidSkepticism %>% standardisation
df_scorecovmis$CovidSkepticism %>% summary
ex <- car::powerTransform(df_scorecovmis$CovidSkepticism+0.0000001)
df_scorecovmis$CovidSkepticism^ex$lambda %>% hist()
df_scorecovmis$CovidSkepticismnorm <-  df_scorecovmis$CovidSkepticism^ex$lambda
df_covmis$CovidSkepticism2 <- df_scorecovmis$CovidSkepticism
df_covmis$CovidSkepticism2norm <-  df_scorecovmis$CovidSkepticism^ex$lambda


```

```{r}
res.aov <- anova_test(CovidSkepticism2norm ~ EXPGRP_TEXT:CONTINENT_BORN_TEXT_1 + HH_INCOME_TEXT + SEX_TEXT + EDUCATION_2_TEXT:DOB_AGE_BRACKET + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)

res.aov
```

```{r}
res.aov <- anova_test(CovidSkepticism2norm ~ demo_class + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)

res.aov
```


##To do mediation analysis


```{r}

```

```{r}

```

```{r}

```

```{r}
write.csv(df_covmis,"./data/mjolnir_clean_v6_Covmis.csv")
```










