---
title: "MJOLNIR_04_CovidMisconception"
author: "Léo HENRY"
date: "4/29/2022"
output: html_document
---


```{r}
library(questionr)
library(FactoMineR)
library(tidyverse)
library(psych)
library(GPArotation)
library(FactoMineR)
library(factoextra)
library(explor)
options(max.print=5000)
```


# data

```{r}
df <- read.csv("./data/mjolnir_clean_v5_AMBI_BIG5.csv")
```


# COV variables

```{r}
df %>% select(matches("^COV((ATT)|(CONSP)|(ORIGIN)|(POLITICS)|(COVERAGE)|(ANTIVACC)|(MEDSKEP))"))
```


```{r}
df_covmis <- df %>%
  mutate(covmis_att_flu=COVATT_1,
         covmis_att_afrDie=COVATT_2,
         covmis_att_eldrNoBgDl=COVATT_3,
         covmis_att_rareNoWorr=COVATT_4,
         covmis_att_bgThrt=COVATT_5,
         covmis_cnsp_ctiusAsian=COVCONSP_1,
         covmis_cnsp_stpCovStpImmi=COVCONSP_2,
         covmis_cnsp_redIntWthChina=COVCONSP_3,
         covmis_cnsp_chnsCovRcst=COVCONSP_4,
         covmis_orgn_covPlnnd=COVORIGIN_1,
         covmis_orgn_covNat=COVORIGIN_2,
         covmis_orgn_covNgeenLab=COVORIGIN_3,
         covmis_orgn_scntFkNwsCov=COVORIGIN_4,
         covmis_pltc_polBgDlIntrst=COVPOLITICS_1,
         covmis_pltc_covNtSerPolSay=COVPOLITICS_2,
         covmis_pltc_polDwnplCovPlpLDngr=COVPOLITICS_3,
         covmis_cvrg_mdiaCovBgrDl=COVCOVERAGE_1,
         covmis_cvrg_nwsGdJbComCov=COVCOVERAGE_2,
         covmis_cvrg_mdiaUseCovMkTrmpRepLkBd=COVCOVERAGE_3,
         covmis_anti_frGovUseCovMndtVacc=COVANTIVACC_1,
         covmis_anti_thnksNoCovVacc=COVANTIVACC_2,
         covmis_anti_covVacEffRedVirus=COVANTIVACC_3)
```

```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_att")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```

```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_cnsp")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```



```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_orgn")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_pltc")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_cvrg")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```




```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_anti")),
               scale.unit=TRUE, ncp=25, graph=T)
explor(res.pca)
```



### HCPM ET CLASSIF 

```{r}
res.mfa <- MFA(df_covmis %>% select(matches("^covmis")) %>% rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}),
               group = c(5,4,4,3,3,3),
               type=c("c","c","c","c","c","c"),
               name.group = c("att","conspiracy","origin","politics","coverage","antivaccin"))
```


```{r}
get_eigenvalue(res.mfa) %>% head
```

```{r}
fviz_screeplot(res.mfa)
```


```{r}
group <- get_mfa_var(res.mfa, "group")

group$coord
group$contrib
# Contribution to the first dimension
fviz_contrib(res.mfa, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa, "group", axes = 2)
```



```{r}
quanti.var <- get_mfa_var(res.mfa, "quanti.var")
quanti.var$contrib
quanti.var$coord
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")
# Contributions to dimension 1
fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
# Contributions to dimension 2
fviz_contrib(res.mfa, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")
```



#### Classification

```{r}
res.hcpc <- HCPC(res.mfa, nb.clust=4, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$quanti
```

```{r}
save(res.mfa, res.hcpc, file='./data/mfa_and_classification.rdata')
```


#### Analysis

```{r}
df_covmis$cov_class <- res.hcpc$data.clust$clust
freq(df_covmis$cov_class)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  ggplot(., aes(y=Covmis_res, x= cov_class, fill=cov_class)) +
  geom_boxplot() +
  facet_wrap(~ Covmis_var, ncol = 5)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_")) %>%
  ggplot(., aes(y=Covmis_res, x= Covmis_var, fill=Covmis_var)) +
  geom_boxplot() +
  facet_wrap(~ cov_class, ncol = 1)
```


```{r}
table(df_covmis$EXPGRP_TEXT, df_covmis$cov_class) %>% prop
```

```{r}
table(df_covmis$CONTINENT_BORN_TEXT_3, df_covmis$cov_class) %>% lprop
```

```{r}
table(df_covmis$HAS_LIVED_USA, df_covmis$cov_class) %>% lprop
```

By considering the data has quatitative and not qualitative we tend to put closer the outsider that might have answered with extreme response in misconsception data and those who answered in the middle. Let's try to see if we get different result when analysing qualitative data.

### MFA and HCPC with qualitative data



```{r}
res_mfa_quali <- df_covmis %>%
  select(matches("^covmis_")) %>%
  transmute_all(~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>% 
  rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}) %>%
  MFA(.,
      group = c(5,4,4,3,3,3),
      type=c("n","n","n","n","n","n"),
      name.group = c("att","conspiracy","origin","politics","coverage","antivaccin"))
```



```{r}
fviz_screeplot(res_mfa_quali)
```



```{r}
fviz_mfa_var(res_mfa_quali, "quali.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
```


```{r}
quali.var <- get_mfa_var(res_mfa_quali, "quali.var")
quali.var$coord
```


#### Cassification

```{r}
res.hcpc <- HCPC(res_mfa_quali, nb.clust=3, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$category
```

```{r}
save(res_mfa_quali, res.hcpc, file='./data/mfa_and_classification_onqualidata.rdata')
```


#### Analysis

##### Boxplot of choice covmis per group

```{r}
df_covmis$covqual_class <- res.hcpc$data.clust$clust
freq(df_covmis$covqual_class)

df_covmis %>%
  transmute_at(.vars = vars(starts_with("covmis")),
               ~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>%
  cbind(df,.) %>%
  mutate(covqual_class=res.hcpc$data.clust$clust) %>%
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_"),
         Covmis_res=factor(Covmis_res,
                           levels = c("+","=","-"))) %>%
  ggplot(., aes(x = covqual_class, fill=Covmis_res)) +
  scale_fill_manual(values=c("green", "blue", "red")) +
  geom_bar(position='fill') +
  facet_wrap(~ Covmis_var, ncol = 5)
```

##### mean of choice covmis per group

```{r}
df_mean_per_cat <- df_covmis %>%
  select(matches("^covmis_")) %>%
  mutate(covmis_cat=df_covmis$covqual_class) %>%
  group_by(covmis_cat) %>%
  summarise_all(mean)
df_mean_per_cat
```

```{r}
map(df_mean_per_cat, std)
sd(c(1,2,)
```

####

```{r}
questionr::freq(df_covmis$covmis_cat)
```






