---
title: "MJOLNIR_04_CovidMisconception"
author: "Léo HENRY"
date: "4/29/2022"
output: html_document
---


```{r}
library(questionr)
library(FactoMineR)
library(tidyverse)
library(psych)
library(GPArotation)
library(FactoMineR)
library(factoextra)
library(explor)
options(max.print=5001)
```


# data

```{r}
df <- read.csv("./data/mjolnir_clean_v5_AMBI_BIG5.csv")
```


# COV variables

```{r}
df %>% select(matches("^COV((ATT)|(CONSP)|(ORIGIN)|(POLITICS)|(COVERAGE)|(ANTIVACC)|(MEDSKEP))"))
```


```{r}
df_covmis <- df %>%
  mutate(covmis_att_flu=COVATT_1,
         covmis_att_afrDie=COVATT_2,
         covmis_att_eldrNoBgDl=COVATT_3,
         covmis_att_rareNoWorr=COVATT_4,
         covmis_att_bgThrt=COVATT_5,
         covmis_cnsp_ctiusAsian=COVCONSP_1,
         covmis_cnsp_stpCovStpImmi=COVCONSP_2,
         covmis_cnsp_redIntWthChina=COVCONSP_3,
         covmis_cnsp_chnsCovRcst=COVCONSP_4,
         covmis_orgn_covPlnnd=COVORIGIN_1,
         covmis_orgn_covNat=COVORIGIN_2,
         covmis_orgn_covNgeenLab=COVORIGIN_3,
         covmis_orgn_scntFkNwsCov=COVORIGIN_4,
         covmis_pltc_polBgDlIntrst=COVPOLITICS_1,
         covmis_pltc_covNtSerPolSay=COVPOLITICS_2,
         covmis_pltc_polDwnplCovPlpLDngr=COVPOLITICS_3,
         covmis_cvrg_mdiaCovBgrDl=COVCOVERAGE_1,
         covmis_cvrg_nwsGdJbComCov=COVCOVERAGE_2,
         covmis_cvrg_mdiaUseCovMkTrmpRepLkBd=COVCOVERAGE_3,
         covmis_anti_frGovUseCovMndtVacc=COVANTIVACC_1,
         covmis_anti_thnksNoCovVacc=COVANTIVACC_2,
         covmis_anti_covVacEffRedVirus=COVANTIVACC_3)
```

```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_att")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```

```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_cnsp")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```



```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_orgn")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_pltc")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```


```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_cvrg")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```




```{r}
res.pca <- PCA(df_covmis %>% select(matches("^covmis_anti")),
               scale.unit=TRUE, ncp=25, graph=T)
#explor(res.pca)
```



### HCPM ET CLASSIF 

```{r}
res.mfa <- MFA(df_covmis %>% select(matches("^covmis")) %>% rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}),
               group = c(5,4,4,3,3,3),
               type=c("c","c","c","c","c","c"),
               name.group = c("att","conspiracy","origin","politics","coverage","antivaccin"))
```


```{r}
get_eigenvalue(res.mfa) %>% head
```

```{r}
fviz_screeplot(res.mfa)
```


```{r}
group <- get_mfa_var(res.mfa, "group")

group$coord
group$contrib
# Contribution to the first dimension
fviz_contrib(res.mfa, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa, "group", axes = 2)
```



```{r}
quanti.var <- get_mfa_var(res.mfa, "quanti.var")
quanti.var$contrib
quanti.var$coord
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")
# Contributions to dimension 1
fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
# Contributions to dimension 2
fviz_contrib(res.mfa, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")
```



#### Classification

```{r}
res.hcpc <- HCPC(res.mfa, nb.clust=4, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$quanti
```

```{r}
save(res.mfa, res.hcpc, file='./data/mfa_and_classification.rdata')
```


#### Analysis

```{r}
df_covmis$cov_class <- res.hcpc$data.clust$clust
freq(df_covmis$cov_class)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  ggplot(., aes(y=Covmis_res, x= cov_class, fill=cov_class)) +
  geom_boxplot() +
  facet_wrap(~ Covmis_var, ncol = 5)

df_covmis %>% 
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_")) %>%
  ggplot(., aes(y=Covmis_res, x= Covmis_var, fill=Covmis_var)) +
  geom_boxplot() +
  facet_wrap(~ cov_class, ncol = 1)
```


```{r}
table(df_covmis$EXPGRP_TEXT, df_covmis$cov_class) %>% cprop
table(df_covmis$EXPGRP_TEXT, df_covmis$cov_class) %>% chisq.test()
```

```{r}
table(df_covmis$CONTINENT_BORN_TEXT_3, df_covmis$cov_class) %>% lprop
```

```{r}
table(df_covmis$HAS_LIVED_USA, df_covmis$cov_class) %>% lprop
```

By considering the data has quatitative and not qualitative we tend to put closer the outsider that might have answered with extreme response in misconsception data and those who answered in the middle. Let's try to see if we get different result when analysing qualitative data.

### MFA and HCPC with qualitative data



```{r}
res_mfa_quali <- df_covmis %>%
  select(matches("^covmis_")) %>%
  transmute_all(~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>% 
  rename_with(function(x){str_remove(x,"^covmis_[A-z]{3,4}_")}) %>%
  MFA(.,
      group = c(5,4,4,3,3,3),
      type=c("n","n","n","n","n","n"),
      name.group = c("att","conspiracy","origin","politics","coverage","antivaccin"))
```



```{r}
fviz_screeplot(res_mfa_quali)
```



```{r}
fviz_mfa_var(res_mfa_quali, "quali.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)
```


```{r}
quali.var <- get_mfa_var(res_mfa_quali, "quali.var")
quali.var$coord
quali.var$contrib
```


#### Cassification

```{r}
res.hcpc <- HCPC(res_mfa_quali, nb.clust=3, graph = T)
```


```{r}
fviz_cluster(res.hcpc,
             repel = TRUE, 
             show.clust.cent = TRUE, 
             palette = "jco", 
             ggtheme = theme_minimal(),
             main = "Factor map"
             )
```



```{r}
res.hcpc$desc.var$category
```

```{r}
save(res_mfa_quali, res.hcpc, file='./data/mfa_and_classification_onqualidata.rdata')
```


#### Analysis

##### Boxplot of choice covmis per group

```{r}
df_covmis$covqual_class <- res.hcpc$data.clust$clust
freq(df_covmis$covqual_class)

df_covmis %>%
  transmute_at(.vars = vars(starts_with("covmis")),
               ~fct_recode(.x %>% as_factor,
                                   "-"="1",
                                   "-"="2",
                                   "="="3",
                                   "="="4",
                                   "+"="5",
                                   "+"="6")) %>%
  cbind(df,.) %>%
  mutate(covqual_class=res.hcpc$data.clust$clust) %>%
  gather(key = "Covmis_var", value="Covmis_res", df_covmis %>% colnames %>% str_detect("^covmis") %>% which) %>%
  mutate(Covmis_var=str_remove(Covmis_var,"^covmis_"),
         Covmis_res=factor(Covmis_res,
                           levels = c("+","=","-"))) %>%
  ggplot(., aes(x = covqual_class, fill=Covmis_res)) +
  scale_fill_manual(values=c("green", "blue", "red")) +
  geom_bar(position='fill') +
  facet_wrap(~ Covmis_var, ncol = 5)
```

##### mean of choice covmis per group

```{r}
df_mean_per_cat <- df_covmis %>%
  select(matches("^covmis_")) %>%
  mutate(covmis_cat=df_covmis$covqual_class) %>%
  group_by(covmis_cat) %>%
  summarise_all(mean)
df_mean_per_cat
```

```{r}
map(df_mean_per_cat, std)

```

####

```{r}
questionr::freq(df_covmis$covmis_cat)
```



```{r}
df_covmis$HH_INCOME_TEXT <- fct_recode(df$HH_INCOME %>% as.character,
"Less than $10,000"="1",
"$10,000 to $30,000"="2",
"$30,000 to $50,000"="3",
"$50,000 to $70,000"="4",
"$70,000 to $100,000"="5",
"$100,000 to $200,000"="6",
"$200,000 to $500,000"="7",
"$500,000 or more"="8")
table(df_covmis$HH_INCOME_TEXT, df_covmis$covqual_class) %>% cprop %>% xtable::xtable()
```


### Demo cluster

```{r}
table(df_covmis$demo_class, df_covmis$covqual_class) %>% cprop
table(df_covmis$demo_class, df_covmis$covqual_class) %>% t.test()

```


## Logistiaue regression

```{r}
library(ordinal)
library(nnet)
library(GGally)
library(gtsummary)
library(ggeffects)
```


We'll do it on the demo classification and then on the other demographic data


```{r}
df_covmis$covqual_class <- factor(df_covmis$covqual_class, c("1","2","3"))
freq(df_covmis$covqual_class)
```


```{r}
df_covmis$demo_class <- df_covmis$demo_class %>% as.factor()
regm <- clm(covqual_class ~ demo_class, data = df_covmis)
summary(regm)
```


```{r}
tbl_regression(regm, exponentiate = TRUE)
```



```{r}
ggcoef_model(
  regm,
  exponentiate = TRUE
)
```


```{r}
plot(ggeffect(regm, "demo_class"))
```



```{r}
df_covmis$covqual_class <-  df_covmis$covqual_class %>%
  as.character() %>%
  as.numeric()
ggboxplot(df_covmis, x="demo_class", y="covqual_class")
res.aov <- anova_test(covqual_class ~ demo_class, data = df_covmis)
res.aov
pwc <- df_covmis %>% tukey_hsd(covqual_class ~ demo_class)
pwc
pwc <- pwc %>% add_xy_position(x = "demo_class")
ggboxplot(df_covmis, x = "demo_class", y = "covqual_class") +
  stat_pvalue_manual(pwc, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )
```

```{r}
df_covmis$covqual_class <- factor(df_covmis$covqual_class, c("1","2","3"))
freq(df_covmis$covqual_class)
```


```{r}
df_covmis$CONTINENT_BORN_TEXT_1 <- relevel(df_covmis$CONTINENT_BORN_TEXT_1 %>% as.factor(), "USA")
df_covmis$DOB_YEAR_PERIODE <- relevel(df_covmis$DOB_YEAR_PERIODE %>% as.factor(), "(1995,2005]")
df_covmis$EDUCATION_2_TEXT <- fct_recode(df$EDUCATION_1 %>% as.character,
          "No college degree"="1",
          "No college degree"="2",
          "No college degree"="3",
          "College degree"="4",
          "College degree"="5",
          "Graduate degree"="6",
          "Graduate degree"="7",
          "Graduate degree"="8")
df_covmis$EDUCATION_2_TEXT %>% freq()

regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + DOB_YEAR_PERIODE + SEX_TEXT + EDUCATION_2_TEXT, data = df_covmis)
summary(regm)
```


```{r}
tbl_regression(regm, exponentiate = TRUE)
```



```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

```{r}
f_normfactor <- function(v){
  res <- AMBI::f_normalisation(v)
  res <- res*3
  res <- cut(res, c(0,1,2,3), labels=c('weak','middle','high'))
  return(res)
}
```



```{r}
df_covmis$neuroticism_qual <- f_normfactor(df_covmis$AMBI_BIG5_Neuroticism)
df_covmis$extraversion_qual <- f_normfactor(df_covmis$AMBI_BIG5_Extraversion)
df_covmis$openness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Openness)
df_covmis$conscientiousness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Conscientiousness)
df_covmis$agreeableness_qual <- f_normfactor(df_covmis$AMBI_BIG5_Agreeableness)
df_covmis$covqual_class <- relevel(df_covmis$covqual_class %>% as.factor(), "2")


regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + DOB_YEAR_PERIODE + SEX_TEXT + EDUCATION_2_TEXT + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)
summary(regm)
```

```{r}
table(df_covmis$EDUCATION_2_TEXT, df_covmis$EXPGRP_TEXT) %>% lprop() %>% xtable::xtable()
```


```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

the variable on the age is long, we shall try to shorten it and cross it with education variable (young people without a college degree are socially different than older on without a college degree)

```{r}
df_covmis$DOB_YEAR_PERIODE <- df_covmis$DOB_YEAR %>% cut(breaks = c(1944,1955,1965,1975,1985,1995,2005))
df_covmis$DOB_AGE_BRACKET <- fct_recode(df_covmis$DOB_YEAR_PERIODE %>% as.character,
          "-25y"="(1995,2005]",
          "25 - 45y"="(1985,1995]",
          "25 - 45y"="(1975,1985]",
          "+45y"="(1944,1955]", 
          "+45y"="(1955,1965]",
          "+45y"="(1965,1975]")
df_covmis <-  df_covmis %>% unite("age_education", c("DOB_AGE_BRACKET","EDUCATION_2_TEXT"))
df_covmis$age_education <- factor(df_covmis$age_education, levels=c('-25y_No college degree',
                                                    "25 - 45y_No college degree",
                                                    '+45y_No college degree', 
                                                    "-25y_College degree", 
                                                    "25 - 45y_College degree",
                                                    "+45y_College degree",
                                                    "-25y_Graduate degree",
                                                    "25 - 45y_Graduate degree",
                                                    "+45y_Graduate degree"))
regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT + age_education + neuroticism_qual + extraversion_qual + openness_qual + conscientiousness_qual + agreeableness_qual, data = df_covmis)
summary(regm)
```

```{r}
ggcoef_multinom(
  regm,
  exponentiate = TRUE
)
```

Now we shall consider only two groups, those in the first and second group, and those in the third group.

```{r}
df_covmis$covqual_class_2 <- fct_recode(df_covmis$covqual_class %>% as.character,
          "Believers"="1",
          "Believers"="2",
          "Skeptics"="3")
freq(df_covmis$covqual_class_2)

reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             age_education + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, data = df_covmis, family = binomial(logit))
reg
```


```{r}
ggcoef_model(reg, exponentiate = TRUE)
```

```{r}
which(is.na(df_covmis$extraversion_qual))
```

```{r}
df_covmis[585,]
```

```{r}
df_covmis2 <-  df_covmis %>% filter((!is.na(CONTINENT_BORN_TEXT_1))) %>%
  filter((!is.na(neuroticism_qual))) %>%
  filter((!is.na(extraversion_qual))) %>%
  filter((!is.na(openness_qual))) %>%
  filter((!is.na(conscientiousness_qual))) %>%
  filter((!is.na(agreeableness_qual)))
which(is.na(df_covmis2 %>% select(EXPGRP_TEXT, CONTINENT_BORN_TEXT_1, HAS_LIVED_USA, SEX_TEXT,
             age_education, neuroticism_qual, extraversion_qual, openness_qual, 
             conscientiousness_qual, agreeableness_qual)), arr.ind=TRUE)
```


```{r}
reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             age_education + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, 
           data = df_covmis2, 
           family = binomial(logit))
step(reg)
```

```{r}
reg <- glm(covqual_class_2 ~ EXPGRP_TEXT + HAS_LIVED_USA + openness_qual, 
           data = df_covmis2, 
           family = binomial(logit))
ggcoef_model(reg, exponentiate = TRUE)
```

```{r}
regm <- multinom(covqual_class ~ EXPGRP_TEXT + CONTINENT_BORN_TEXT_1 + HAS_LIVED_USA + SEX_TEXT +
             EDUCATION_2_TEXT + DOB_AGE_BRACKET + neuroticism_qual + extraversion_qual + openness_qual + 
             conscientiousness_qual + agreeableness_qual, 
           data = df_covmis2)
step(regm)
```



```{r}
regm <- multinom(covqual_class ~ EXPGRP_TEXT + HAS_LIVED_USA + 
    SEX_TEXT + openness_qual + agreeableness_qual, 
           data = df_covmis2)
stargazer::stargazer(regm)
ggcoef_multinom(regm, exponentiate = TRUE)
```


























